\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
     \usepackage[svgnames]{xcolor}
    \usepackage{hyperref}
\definecolor{my_blue}{RGB}{10,90,178}
\hypersetup{
    colorlinks=true,
    linkcolor=my_blue,
    filecolor=magenta,      
    urlcolor=my_blue,
}


\urlstyle{same}
    \textheight=10in
    \pagestyle{empty}
    \raggedright

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\vspace*{-40pt}



%==== Profile ====%
\vspace*{-10pt}
\begin{center}
    {\Huge \scshape {Krushna Panchvishe}}\\
    Pune, MH $\cdot$ \href{mailto:krushna.4997@gmail.com}{krushna.4997@gmail.com} $\cdot$ +91-9422465915 $\cdot$ \href{https://github.com/krushna2500}{github.com/krushna2500} \href{https://www.linkedin.com/in/krushna-panchvishe-ba0b6513a/}{linkedin.com/in/krushna2500}\\
\end{center}
\header{Experience}

\vspace{1mm}
\textbf{Codeblaze Solutions Pvt Ltd} \hfill Pune\\
\textit{DevOps Engineer/AWS Cloud Architect} \hfill Set 2024 - Present\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt

    \item Designed, implemented, and maintained scalable cloud infrastructure on AWS, automating deployments and operationalizing AI/ML models to ensure high availability and performance across production-grade environments.
    \item Implemented Infrastructure as Code (IaC) using Terraform and CloudFormation to standardize and automate the provisioning and management of cloud resources.
    \item Built and optimized Kubernetes clusters for container orchestration, ensuring efficient resource utilization and seamless application scaling.
    \item Collaborated with cross-functional teams to streamline cloud architecture, improve scalability, and maintain security best practices, including \textbf{IAM policy enforcement} and \textbf{least privilege principles} for AWS resources.
    \item Implemented monitoring and logging solutions using AWS CloudWatch, Prometheus, and Grafana, allowing proactive issue detection and resolution in production environments.
    \item Managed cloud security practices by configuring firewalls, VPCs, subnets, and conducting vulnerability assessments to mitigate security risks across cloud infrastructure.
    \item Operationalized machine learning models by integrating CI/CD pipelines for model deployment, and automating the continuous training and retraining of models in production.
    \item Designed, trained, and deployed a Text-to-SQL model on AWS SageMaker, enabling automated database query generation from natural language inputs, improving data accessibility for non-technical users.
    \item Implemented centralized repository management systems such as Nexus, JFrog, and GitLab Container Registries to enhance the development and deployment pipeline.
    \item Automated operational tasks using Python and Bash scripts, improving efficiency and reducing manual intervention in cloud and machine learning environments.    
    % \item 
          % 	Entities and relations are stored in graph database.
    %\item Implemented perspective based sentiment analysis using Zero Shot Learning. Explanation can be found \href{ https://twitter.com/aakashb_95/status/1491459132897263617?s=20&t=wXTHKhBcILYE4LebSDFZlQ}{here}.
          % 	\item Trained a Named Entity Recognition model using SpaCy. Used RoBERTa-base model on a \textbf{custom dataset in BIO format to achieve an F1 score of 84.9\%} on 20 tags (Ontonotes5.0 + two custom tags).
\end{itemize}

\vspace*{2mm}

\vspace{1mm}
\textbf{Centre for Development of Advanced Computing (C-DAC)} \hfill Pune\\
\textit{Project Engineer (DevOps/MLOps) - Applied AI Group} \hfill Oct 2021 - Sep 2024\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
    \item Design, implement, and maintain the CI/CD pipeline to enable automated build, test, and deployment of software applications resulted in improving application delivery speed as well as reduction in deployement cost by \textbf{60\%}
    \item Established CI/CD pipelines with Jenkins, GitLab CI/CD, and AWS CodePipeline for efficient and automated software delivery.Implement and enforce best practices for version control, code merging, and branching strategies.
    \item Implemented IAM policies to enforce the principle of least privilege and enhance security across AWS projects.
    \item Collaborated with development teams to optimize build processes and improve code quality using code analysis and testing tools.
    \item Worked on automated VAPT(SAST) report generation and guided teams to resolve them. 
    \item Managed Gitlab(EE) Administration for whole project. i.e. finalizing folder structure, account management, branching strategies, etc.
    \item Setup and Implementation of centralised repository management tools from scratch like Nexus, JFrog, Container and package registries in Gitlab EE.
    \item Configured and managed VPCs, subnets, and firewalls to ensure secure and efficient communication between AWS resources.
    \item Implemented monitoring and alerting solutions using differnet tools for proactive issue identification and resolution.
    \item Collaborated with development teams to optimize applications for AWS cloud environments, ensuring scalability and high availability.
    \item Designed and implemented Ansible playbooks for automated configuration management, resulting in a \textbf{40\%} reduction in deployment time and ensuring consistent infrastructure across a heterogeneous environment.
    \item Automated routine tasks using scripting languages (Python, Bash) to improve operational efficiency.
    \item Configured and managed Docker containers for application deployment, orchestrating them using Swarm/Kubernetes.
    % \item 
          % 	Entities and relations are stored in graph database.
    %\item Implemented perspective based sentiment analysis using Zero Shot Learning. Explanation can be found \href{ https://twitter.com/aakashb_95/status/1491459132897263617?s=20&t=wXTHKhBcILYE4LebSDFZlQ}{here}.
          % 	\item Trained a Named Entity Recognition model using SpaCy. Used RoBERTa-base model on a \textbf{custom dataset in BIO format to achieve an F1 score of 84.9\%} on 20 tags (Ontonotes5.0 + two custom tags).
\end{itemize}

\vspace*{2mm}

%==== Education ====%
\header{Education}
\textbf{Centre for Development of Advanced Computing (C-DAC)}\hfill Pune\\
PG Diploma Artificial Intelligence - \textit{Grade: A} \hfill Mar 2021 - Sep 2021\\
\vspace{2mm}
\textbf{Bhivarabai Sawant Institute of Technology and Research}\hfill Pune\\
B.E. Computer Engineering - \textit{72\%} \hfill Aug 2014 - Jul 2018\\
\vspace{2mm}

\header{Projects}

% ----------------------------

{\textbf{Human- Robot Interaction using point bug algorithm and android.}}
%{\sl ESP8266, C++, Arduino IDE} \\
\begin{itemize} \itemsep 1pt
          % \item Analyzed gene expression sequences from The Cancer Genome Atlas (TCGA) database for 33 different Cancer types and Solid Tissue Normals.
    \item The entire assignment/project is advanced in such a manner that it's far capable of \textbf{traversing to the target area through avoiding all kinds of boundaries and shifting on an optimized route} and main to large results both concerning time and electricity.
          % Performed EDA, tested hypothesis to find relations between a particular gene and cancer type. 
          % % \item Obtained insights about gene behaviour/activity-inactivity and validated existing facts(one to many relation of genes to cancer) using statistical techniques.
          % \item Reduced features using PCA, Cosine Similarity and UMAP.
          \\
\end{itemize}
\vspace*{2mm}

%----------------- CMM --------------------
%{\sl FastAi, PyTorch} 
%\hfill \url{https://github.com/aakashb95/car-detection}\\
\begin{itemize} \itemsep 1pt
    \item \href{https://github.com/krushna2500/spellchecker}{\textbf{Spellchecker}}
    The idea is to build a spellchecker which works on proper noun. We build it sucessfully but this is failure because we don't have control over phonetic(proper nouns are not universal like english words)
    \item Docker Hub: \href{https://hub.docker.com/r/krushna2500/spellchecker}{\textbf{Spellchecker Image}} Dockerized the application and deployed it on an AWS amplify.
\end{itemize}
\vspace*{2mm}
%-----------------------------------

%=========== WiFi Switch ============
% {\textbf{ESP8266 WiFi switch [WIP]}} 
% %{\sl ESP8266, C++, Arduino IDE} \\
% \begin{itemize} \itemsep 1pt
% \item Used ESP8266 to connect to an MQTT server using Wi-Fi to control a tubelight.
% \item Implemented Wi-Fi modules and added a functionality to take input from an Infrared remote if Wi-Fi stops working.
% \\
% \end{itemize}
% \vspace*{2mm}
%===================================

%--languages and technologies--%
\header{Tools and Technologies}
\begin{itemize}
    \item \textbf{VCS and SCM} : Git, SVN, Gitlab, Github
    \item \textbf{CI/CD} : Gitlab CI, Jenkins 
    \item \textbf{Repository Manager} : Nexus, JFrog, Package and Container Registries In Gitlab(EE)
    \item \textbf{Containerization and orchestration} : Docker, Docker Swarm, Kubernetes, Terraform
    \item \textbf{Build Tools} : Poetry, Pip, Maven, Npm
    \item \textbf{Cloud} : AWS/AZURE
    \item \textbf{Monitoring} : Promitheus, Grafana, Elastic Stack, Zabbix 
    \item \textbf{MLOps} : DVC, MLflow, Wandb
    \item \textbf{Scripting Languages} : Python, Bash, Powershell
    \item \textbf{Configuration Management Tools} : Ansible, Puppet
    \item \textbf{Others} : Linux, Kafka, MinIo, Nginx
          % \item Oracle SQL, ArangoDB
    % \item Numpy, Pandas, Scikit-learn, Pytorch, SpaCy, HuggingFace
    % \item Git, FastAPI, Streamlit, Docker
\end{itemize}

%\begin{tabular}{ l l }
%	Programming Languages: & C++, Python                         \\
%	Database:              & Oracle SQL, MySQL                          \\
%	Frameworks:            & PyTorch, FastAi                            \\
%	Libraries:             & Numpy, Pandas, scikit-learn                \\
%	Tools:                 & Git, AWS (EC2), Azure (Compute, ML studio) \\
%\end{tabular}
\vspace{2mm}

\
\end{document}